---
title: "Ocean Example"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,cache=TRUE)
```

```{r packages,message=FALSE}
library(ggplot2)
library(colorRamps)
library(gridExtra)
library(DiceKriging)
library(DiceDesign)
library(hetGP)
library(MCMCpack)
library(lhs)
library(mvtnorm)
```

We load the simulator and some useful functions.
```{r fksettings}
source("SimulatorAndFunctions.R")
```

The seed is set for replication:
```{r seed}
set.seed(123)
```



## Emulation

### Static design

We start with a space filling design and we make $20$ replicates at each unique location.
```{r space filling design}
n = 50
X0 = lhsDesign(n,2)
X0 = maximinSA_LHS(X0$design)$design
X <- rbind(X0, X0, X0, X0, X0, X0, X0, X0, X0, X0)
X <- rbind(X, X)
Z <- apply(X, 1, simulator)
```

The input domain is normalized in $[0,1]^2$. We center and reduce the outputs. 
```{r normalization}
Zm <- mean(Z)
Zv <- var(Z)
Z <- (Z - Zm)/sqrt(Zv)
```

These are the settings for computing homoskedastic and heteroskedastic GPs.
```{r GP settings}
# settings for GPs
lower <- rep(0.01, 2)
upper <- rep(30, 2)
covtype <- "Matern5_2"
nc <- list(g_min=1e-6, g_bounds=c(1e-6, 1), # k_theta_g_bounds=c(1,10), 
           lowerDelta=log(1e-6))
settings <- list(linkThetas="none", logN=TRUE, initStrategy="smoothed", 
                 checkHom=TRUE, penalty=TRUE, trace=0, return.matrices=TRUE, return.hom=FALSE)
control <- list(tol_dist=1e-4, tol_diff=1e-4, multi.start=30)
```

Then, they are fitted on the data:
```{r GP fit}
## Homoskedastic
Ghom <- mleHomGP(X, Z, lower=lower, upper=upper, covtype=covtype,
                known=list(beta0=0), maxit=1000) 

## Heteroskedastic 
Ghet <- mleHetGP(X, Z, lower=lower, upper=upper, covtype=covtype, 
                noiseControl=nc, settings=settings, known=list(beta0=0), maxit=1000)

```

### Sequential design


We use the static design as the initial design but we only use $10$ replicates instead of $20$. The remaining points are added sequentially.

```{r seqdesign}
ninitseq = 10
n=nrow(X0)
Xseq <- X[1:(ninitseq*n),]
Y <- Z[1:(ninitseq*n)]
mod <- mleHetGP(Xseq, Y, lower=lower, upper=upper, covtype=covtype, 
                noiseControl=nc, settings=settings, known=list(beta0=0), maxit=1000)

nadd = nrow(X)-nrow(Xseq)  

h <- rep(NA, nadd)
## acquisitions
for(i in 1:nadd) { 
  
  ## choose lookahead horizon and solve IMSPE
  h[i] <- horizon(mod)
  opt <- IMSPE_optim(mod, h[i], control=control)
  cat("i=", i, ", h=", h[i], "\n", sep="")
  
  ## evaluate the simulator
  ynew <- (simulator(opt$par) -Zm)/sqrt(Zv)
  
  ## update the fit
  mod <- update(mod, Xnew=opt$par, Znew=ynew, ginit=mod$g*1.01)
  if(i %% 25 == 0){
    mod2 <- mleHetGP(list(X0=mod$X0, Z0=mod$Z0, mult=mod$mult),
                     Z=mod$Z, lower=lower, upper=upper, covtype=covtype, 
                     noiseControl=nc, settings=settings, known=list(beta0=0), 
                     maxit=1000)
    if(mod2$ll > mod$ll) mod <- mod2  
  }
}
seqGhet=mod
```


### Results

Prediction on a grid
```{r grid}
de = as.matrix(expand.grid(seq(0,1,.01),seq(0,1,.01)))
predHomde = predict(x = de, object = Ghom)
gridHom = as.data.frame(cbind(de[,1:2],predHomde$mean,predHomde$sd2,predHomde$nugs,sqrt(predHomde$sd2 + predHomde$nugs)))
names(gridHom) = c("long","lat","mean","varmean","nug","psd")
predhetde = predict(x = de, object = Ghet)
gridhet = as.data.frame(cbind(de[,1:2],predhetde$mean,predhetde$sd2,predhetde$nugs,sqrt(predhetde$sd2 + predhetde$nugs)))
names(gridhet) = c("long","lat","mean","varmean","nug","psd")
designseq = as.data.frame(cbind(mod$X0,mod$mult))
names(designseq) = c("long","lat","rep")
predhetseqde = predict(x = de, object = mod)
gridhetseq = as.data.frame(cbind(de[,1:2],predhetseqde$mean,predhetseqde$sd2,predhetseqde$nugs, sqrt(predhetseqde$sd2 + predhetseqde$nugs)))
names(gridhetseq) = c("long","lat","mean","varmean","nug","psd")
gridHom$mean = gridHom$mean * sqrt(Zv) + Zm
gridHom$varmean = gridHom$varmean * Zv
gridHom$psd = gridHom$psd * sqrt(Zv)
gridHom$nug = gridHom$nug * Zv
gridhet$mean = gridhet$mean * sqrt(Zv) + Zm
gridhet$varmean = gridhet$varmean * Zv
gridhet$psd = gridhet$psd * sqrt(Zv)
gridhet$nug = gridhet$nug * Zv
gridhetseq$mean = gridhetseq$mean * sqrt(Zv) + Zm
gridhetseq$varmean = gridhetseq$varmean * Zv
gridhetseq$psd = gridhetseq$psd * sqrt(Zv)
gridhetseq$nug = gridhetseq$nug * Zv
```

Plots for homGP
```{r plot homgp}
ggplot(gridHom, aes(long, lat)) + geom_raster(aes(fill = mean), interpolate = TRUE) + scale_fill_gradientn(colours=matlab.like(10),limits=c(min(gridHom$mean,gridhet$mean),max(gridHom$mean,gridhet$mean)))
ggplot(gridHom, aes(long, lat)) + geom_raster(aes(fill = psd), interpolate = TRUE)+ scale_fill_gradientn(colours=matlab.like(10),limits=c(min(gridHom$psd,gridhet$psd),max(gridHom$psd,gridhet$psd)))
```

Plots for hetGP
```{r plot hetgp}
ggplot(gridhet, aes(long, lat)) + geom_raster(aes(fill = mean), interpolate = TRUE) +scale_fill_gradientn(colours=matlab.like(10),limits=c(min(gridHom$mean,gridhet$mean),max(gridHom$mean,gridhet$mean)))
ggplot(gridhet, aes(long, lat)) + geom_raster(aes(fill = psd), interpolate = TRUE)+ scale_fill_gradientn(colours=matlab.like(10),limits=c(min(gridHom$psd,gridhet$psd),max(gridHom$psd,gridhet$psd)))
```


Plots for SeqhetGP

```{r plot seqhetgp}
ggplot(gridhetseq, aes(long, lat)) + geom_raster(aes(fill = mean), interpolate = TRUE) + scale_fill_gradientn(colours=matlab.like(10))
ggplot(gridhetseq, aes(long, lat)) + geom_raster(aes(fill = mean), interpolate = TRUE) + scale_fill_gradientn(colours=matlab.like(10))+geom_point(data=designseq,aes(x=long,y=lat,colour=rep))+scale_color_gradient(low="grey", high="black")
ggplot(gridhetseq, aes(long, lat)) + geom_raster(aes(fill = psd), interpolate = TRUE)+ scale_fill_gradientn(colours=matlab.like(10))+geom_point(data=designseq,aes(x=long,y=lat,colour=rep))+scale_color_gradient(low="grey", high="black")
ggplot(gridhetseq, aes(long, lat)) + geom_raster(aes(fill = psd), interpolate = TRUE)+ scale_fill_gradientn(colours=matlab.like(10))+geom_text(data=designseq,aes(x=long,y=lat,label=rep))
```


### Comparaison of prediction

```{r load data test2}
load("testdesign2D.Rdata")
#vmNorm = (vm-Zm)/sqrt(Zv)
library(hetGP)
#Hom GP
predhom = predict(x = testdesign, object = Ghom)
#Het GP
predhet = predict(x = testdesign, object = Ghet)
#Het GP seq
predHetseq = predict(x = testdesign, object = mod)
# RMSE
Ztest.true = (vm - Zm)/sqrt(Zv)
summary(Ztest.true)
summary(predHetseq$mean)
msehom = mean(((predhom$mean-Ztest.true))^2)
msehet = mean(((predhet$mean-Ztest.true))^2)
msehetseq = mean(((predHetseq$mean-Ztest.true))^2)
# scores
schom = mean(-(Ztest.true-predhom$mean)^2/(predhom$sd2) -log(predhom$sd2))
schet = mean(-(Ztest.true-predhet$mean)^2/(predhet$sd2) -log(predhet$sd2))
schetseq = mean(-(Ztest.true-predHetseq$mean)^2/(predHetseq$sd2) -log(predHetseq$sd2))
# scores 2
Ztest = (apply(testdesign,1,simulator)-Zm)/sqrt(Zv) # for computing scores
schom2 = mean(-(Ztest-predhom$mean)^2/(predhom$sd2+predhom$nugs) -log(predhom$sd2+predhom$nugs))
schet2 = mean(-(Ztest-predhet$mean)^2/(predhet$sd2+predhet$nugs) -log(predhet$sd2+predhet$nugs))
schetseq2 = mean(-(Ztest-predHetseq$mean)^2/(predHetseq$sd2+predHetseq$nugs) -log(predHetseq$sd2+predHetseq$nugs))
```


We compute the mean square error, the score on the mean prediction and the score for a prediction of an output of the simulator.
```{r results}
c(rmsehom=msehom,rmsehet=msehet,rmsehetse=msehetseq)
c(scorehom=schom,scorehet=schet,scorehetse=schetseq)
c(scorehom=schom2,scorehet=schet2,scorehetse=schetseq2)
```





## Calibration


### Simulation for field data 

```{r sim field data}
n = 150
X0 = lhsDesign(n,2)
X0 = maximinSA_LHS(X0$design)$design
u1 = (700 -100)/900  
u2 = (200- 100)/900
Xfield = cbind(X0,u1,u2)
library(parallel)
Yfield = mclapply(1:n,function(i)
{
  mean(sapply(1:200,function(k) simulator4d(Xfield[i,])))
},mc.cores = 10)
Yfield = Reduce(c,Yfield)
vareps = 2^2 
Yfieldnoise = Yfield + rnorm(length(Yfield),0,sd=sqrt(vareps)) 
```


### Emulation for calibration

```{r emulation calib}
source("function_LHD_optim_grid.R")
b_inf_theta=c(0,0)
b_sup_theta=c(1,1)
size_design = 500

out = GRID_design(Xfield[,1:2],b_inf_theta,b_sup_theta,size_design)
out_opt=maximinSA_LHS_grid(out,dim_xf=2,c=0.95,dim_theta=2,Imax=2000)
#10 replicates
Xsim = matrix(rep(t(out_opt),10),ncol=4,byrow = T)
Ysim = apply(Xsim,1,simulator4d)

covtype <- "Matern5_2"
noiseControl <- list(g_min=1e-6, g_bounds=c(1e-6, 1), lowerDelta=log(1e-6))
settings <- list(linkThetas="none", initStrategy="smoothed", return.hom=TRUE)
lower <- c(0.01, 0.01, 0.001, 0.001) 
upper <- c(30, 30, 100, 100) 

het <- mleHetGP(Xsim, Ysim, lower=lower, upper=upper, covtype=covtype, noiseControl=noiseControl, 
                settings=settings, maxit=10000)
hom <- het$modHom
```


### Calibration

After defining the likelihood function, we run an MCMC sampler.

```{r calibration}
lpost.invert <- function(theta, XF, yF, GP)
{
  ## input processing and checking
  if(length(theta) != ncol(GP$X0) - ncol(XF) + 1) 
    stop("length(theta), ncol(XF), ncol(GP$X0) mismatch")
  u <- theta[-length(theta)]
  s2 <- theta[length(theta)]
  
  ## prior checking  
  if(any(u < 0 | u > 1)) return (-Inf)
  if(s2 < 0) return(-Inf)
  
  ## derive predictive distribution for XF paired with u
  XFU <- cbind(XF, matrix(rep(u, nrow(XF)), ncol=length(u), byrow=TRUE)) 
  p <- predict(GP, XFU, xprime=XFU)
  C <- s2*diag(nrow(p$cov)) + (p$cov + t(p$cov))/2 
  
  ## gaussian log density evaluation for yF under that predictive
  return(dmvnorm(yF, p$mean, C, log=TRUE) - log(s2))
}


V <- diag(c(0.01, 0.005, 0.05))
calHom <- MCMCmetrop1R(lpost.invert, XF=Xfield[,1:2], yF=Yfieldnoise, GP=hom, logfun=TRUE, theta.init=c(0.5,0.5,1), 
                       burnin=1000, mcmc=2e4, V=V)

calHet <- MCMCmetrop1R(lpost.invert, XF=Xfield[,1:2], yF=Yfieldnoise, GP=het, logfun=TRUE, theta.init=c(0.5,0.5,1), 
                       burnin=1000, mcmc=2e4, V=V)
```

```{r cal plots}
dfcalhom = as.data.frame(calHom)
names(dfcalhom) = c("u1","u2","s2")
dfcalhom[,1:2] = dfcalhom[,1:2] * 900 +100
hom1 = ggplot(dfcalhom,aes(x=u1,stat(density))) + geom_density() + theme_bw() + xlim(50,1000) + geom_vline(aes(xintercept=700),color="red")
hom2 = ggplot(dfcalhom,aes(x=u2,stat(density))) + geom_density() + theme_bw() +xlim(50,1000)  + geom_vline(aes(xintercept=200),color="red")
hom3 = ggplot(dfcalhom,aes(x=s2,stat(density))) + geom_density() + theme_bw() + xlim(1,7) + geom_vline(aes(xintercept=4),color="red")
dfcalhet = as.data.frame(calHet)
names(dfcalhet) = c("u1","u2","s2")
dfcalhet[,1:2] = dfcalhet[,1:2] * 900 +100
het1 = ggplot(dfcalhet,aes(x=u1,stat(density))) + geom_density() + theme_bw() + xlim(50,1000) + geom_vline(aes(xintercept=700),color="red")
het2 = ggplot(dfcalhet,aes(x=u2,stat(density))) + geom_density() + theme_bw() + xlim(50,1000) + geom_vline(aes(xintercept=200),color="red")
het3 = ggplot(dfcalhet,aes(x=s2,stat(density))) + geom_density() + theme_bw() + xlim(1,7) + geom_vline(aes(xintercept=4),color="red")
grid.arrange(arrangeGrob(hom1,hom2,hom3,top="homGP",ncol=3),arrangeGrob(het1,het2,het3,top="hetGP",ncol=3),nrow=2,ncol=1)
```




### Calibration from a sequential design


```{r init seq}
#8 replicates kept
Xsim.init = Xsim[1:(8*size_design),]
Ysim.init = Ysim[1:(8*size_design)]

covtype <- "Matern5_2"
noiseControl <- list(g_min=1e-6, g_bounds=c(1e-6, 1), lowerDelta=log(1e-6))
settings <- list(linkThetas="none", initStrategy="smoothed", return.hom=FALSE)
lower <- c(0.01, 0.01, 0.001, 0.001) 
upper <- c(30, 30, 100, 100) 

mod <- mleHetGP(Xsim.init, Ysim.init, lower=lower, upper=upper, covtype=covtype, noiseControl=noiseControl, 
                settings=settings, maxit=10000)
```



```{r seq design}
Xseq = Xsim.init
Yseq = Ysim.init
nadd = nrow(Xsim)-nrow(Xseq)  


h <- rep(NA, nadd)
## acquisitions
for(i in 1:nadd) { 
  
  ## choose lookahead horizon and solve IMSPE
  h[i] <- horizon(mod)
  opt <- IMSPE_optim(mod, h[i], control=control)
  cat("i=", i, ", h=", h[i], "\n", sep="")
  
  ## evaluate the simulator
  ynew <- simulator4d(opt$par)
  
  ## update the fit
  mod <- update(mod, Xnew=opt$par, Znew=ynew, ginit=mod$g*1.01)
  if(i %% 25 == 0){
    mod2 <- mleHetGP(list(X0=mod$X0, Z0=mod$Z0, mult=mod$mult),
                     Z=mod$Z, lower=lower, upper=upper, covtype=covtype, 
                     noiseControl=nc, settings=settings, known=list(beta0=0), 
                     maxit=1000)
    if(mod2$ll > mod$ll) mod <- mod2  
  }
}
seqGhet = mod
```


